### 2015-01-09 paper/Content/sources.tex
Added missing sources for 'building blocks'

>>>>

\bibitem{SDKActivities}
Google Inc., \emph{Android Developers -- Activities},
[Online]. http://developer.android.com/guide/components/activities.html (retrieved 05-Jan-2015)

\bibitem{SDKFragments}
Google Inc., \emph{Android Developers -- Fragments},
[Online]. http://developer.android.com/guide/components/fragments.html(retrieved 05-Jan-2015)
